---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "A Reconsideration of Money Growth Rules"
subtitle: "Replication Projet"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Jessica van der Berg"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch Univeristy, South Africa" # First Author's Affiliation
Email1: "20190565\\@sun.ac.za" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "MCMC \\sep DSGE \\sep Money Growth rules" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

Adding additional latex packages:
# header-includes:
    -\usepackage{colortbl}
    - \usepackage{graphicx}
    - \usepackage{caption}
    - \usepackage{float}
    - \usepackage{subfig}
    - \usepackage{subcaption} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  The reports builds on a research paper submitted by Johannes Coetsee, Jessica Van der Berg and Cassandra Pengelly in May 2021. This reports sets out to simulate, estimate, analyze and compare the Taylor rule, Constant Money Growth rule and Flexible Money Growth rule. The paper concludes that the flexible money growth rules preforms similarly to the Taylor rule during 1982 - 2019. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

library(readxl)
obss <- read_excel("C:/Users/jesic/OneDrive/Desktop/Studies 2021/Second Semester/Time series/Project Lu/obss.xlsx")
pacman::p_load(tidyverse)
library(ggplot2)


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

Central banks implement monetary policy usually by manipulating the nominal interest rate, otherwise known as the Taylor rule. The Taylor rule offers many advantages including easy communication that boost investors and the publics confidence in the central bank. However, it has been argued that the Taylor rule should be used as a mere benchmark, and that not doing so can lead to poor economic outcomes. @belongia2019reconsideration argue that constant and flexible money growth rules can be as effective in stabilizing inflation and output in a low interest rate environment, and in certain cases, can outperformed the historically preferred Taylor rule. 

@belongia2019reconsideration estimate a New Keynesian model using Bayesian methods. Bayesian methods create the opportunity for researchers to evaluate macroeconomic models that frequentist econometrics find challenging. A popular macroeconomic model that economist estimate using Bayesian methods is dynamic stochastic general equilibrium (DSGE) model. In the past, classical optimization methods were used to estimate DSGE models, however, Bayesian methods are preferred due to the wide variety of tools that research can make use of to estimate and evaluate DSGE models. Bayesian methods also have the advantage of increasing computing power meaning that more complicated DSGE models can be estimated @guerron2013bayesian. 

By estimating a New Keynesian model, @belongia2019reconsideration reconsiders money growth rules. This is accomplished by identifying a parsimonious rule that dictates a systematic response of money growth to changes in the output gap. Further, simulations are performed to assess how the United States (US) economic have preformed over the sample period from 1983 through 2019 and the feasibility of the money growth rule.  The simulations shows that the money growth rule preforms satisfactory during the entire sample period, including during the Great Recession and its aftermath. @belongia2019reconsideration found that money growth rules offer more flexibility that leads to a decrease in volatility in output growth and inflation.  Implementing a flexible money growth rate rule would have allowed the US economy to recover faster from the Great Recession and the  2008/2009 financial crisis. 

This report sets out to replicate the estimation results of @belongia2019reconsideration. However, this paper deviates from the @belongia2019reconsideration paper by focusing on the full sample of quarterly data from 1983 to 2019, instead of examining low interest rate environments. Therefore, instead of estimating and comparing policy rules for low-interest rates environments specifically, this report compares different simulated models over the entire sample period, thereby assessing the relative strengths of policy rules regardless of the economic environment. This report sets out to simulate, analyse and compare three New Keynesian models to evaluate the Taylor rule, Constant Money Growth rule and a Flexible Money Growth rule. The comparisons will be visualized and summarized with, amongst others, Impulse Response Functions (IRFs), multivariate convergence diagnostics, and Monte Carlo Markov Chain (MCMC) diagnostics. My findings largely support the results of @belongia2019reconsideration, with the main conclusion being that the flexible money growth rules preform similarly to the Taylor rule during the sample. This finding supports the argument of a possible reconsideration of incorporating flexible money growth rules in the Fed’s monetary policy toolkit.

The rest of the paper is structured as followed: Section 2 briefly outlines the model\footnote{The replication, analysis and discussion of the model can be found in the first submission that was submitted by Johannes Coetsee, Jessica Van der Berg and Cassandra Pengelly in May 2021.}. Section 3 discusses the data as well as the calibration and the priors. Section 4  discusses the estimation results of the model, including the posterior distribution estimations and the impulse response functions. Section 5 provides an in-dept discussion regarding several diagnostic test that were carried out in order to asses the DSGE mode. Finally, section 6 concludes. 

\newpage

# The Model
The model economy includes four economic agents: a representative household, a representative finished goods-producing firm, an intermediate goods-producing firm, and a central bank.  The equations are then simplified and linearized. An in-dept discussion about the model can be found in the first submission, however, this section describes the final equations that were log-linearized around the steady-state to describe how the economy responds to shocks.

1. Linearized Household Budget Constraint
\begin{align*} \notag
\hat{y_t} =\hat{c_t}
\end{align*}

2. Linearized Consumption Euler Equation:
\begin{align} \notag
(z - \beta\gamma)(z-\gamma)\hat{\lambda_t} = \gamma z \hat{y_{t-1}} - (z^2 + \beta\gamma^2)\hat{y_t} + \beta\gamma E_t \hat{y_{t+1}} + (z -\beta\gamma\rho_a)(z-\gamma)\hat{a_t} - \gamma z\hat{z_t}
\end{align}

3. Linearized Bonds Euler Equation:
\begin{align*} \notag
\hat{\lambda}_t = \hat{r}_t + E_t \hat{\lambda}_{t+1} - E_t \hat{\pi}_{t+1}
\end{align*}

4. Linearized Efficient Level of Output:
\begin{align} \notag
0 = \gamma z \hat{q_{t-1}} - (z^2 + \beta\gamma^2)\hat{q_t} + \beta\gamma z E_t\hat{q_{t+1}} + \beta\gamma(z-\gamma)(a-\rho_a)\hat{a_t} - \gamma z\hat{z_t} 
\end{align}

5. Linearized Output Gap:
\begin{align} \notag
\hat{x}_{t}&=\hat{y}_{t}-\hat{q}_{t} 
\end{align}


6. Linearized Philips Curve:
\begin{align*} \notag
(1+\beta \alpha)\hat{\pi_t} = \alpha \hat{\pi}_{t-1} + \beta E_t \hat{\pi}_{t+1} - \psi\hat{\lambda}_t + \psi\hat{a}_t + \hat{e}_t
\end{align*}

7. Linearized Taylor Rule:
\begin{align} \notag
\hat{r}_{t}= \rho_{r}\hat{r}_{t-1}  + \rho_{\pi}\hat{\pi}_{t} + \rho_{x}\hat{x}_{t} + \varepsilon_{rt} 
\end{align}

8. Linearized Money Euler Equation:
\begin{align} \notag
{\frac{1}{\delta}}[&-{\hat{m_t}}+{\hat{u_t}}]-{\phi_m}{\hat{z_t}}+{\beta}{\phi_m}{E_t}{\hat{m}_{t+1}}-(1+\beta){\phi_m}{\hat{m_t}}+{\phi_m}{\hat{m_{t-1}}} \notag \\
&={\frac{\delta_r}{\delta}}(r-1){\hat{\lambda_t}}+{\frac{\delta_r\hat{r_t}}{\delta}}-\frac{\delta_r}{\delta}(r-1){\hat{a_t}}-{\hat{m_t}}+{\hat{u_t}}\notag\\
&-{\phi_m}{\delta}{\hat{z_t}}+{\beta}{\phi_m}{\delta}{E_t}{\hat{m}_{t+1}}-({1+\beta}){\phi_m}{\delta}{\hat{m_t}}+{\phi_m}{\delta}{\hat{m}_{t-1}} \notag
\end{align}

9. Linearized Nominal Money Growth:
\begin{align} \notag
\hat{\mu}_{t}=\hat{m}_{t}-\hat{m}_{t-1}+\hat{z}_{t}+\hat\pi_{t} 
\end{align}

10. Linearized Output Growth:
\begin{align} \notag
\hat{g}_{t}&=\hat{y}_{t}-\hat{y}_{t-1}+\hat{z}_{t} 
\end{align}

11. Linearized Preference Shock:
\begin{align} \notag
\ln (a_t) &= \rho_a \ln (a_{t-1}) + \varepsilon_{a_{t}} \notag \\
\hat{a_{t}} &= \rho_{a} \hat{a_{t-1}}+ \varepsilon_{a_{t}} \notag
\end{align}

12. Linearized Productivity Shock with a Random Walk: 
\begin{align} \notag
\hat{z_t} &= \varepsilon_{z_{t}}
\end{align}

13. Linearized Money Demand Shock: 
\begin{align*} \notag
ln (u_t)&= \rho_u \ln (u_{t-1})+ \varepsilon_{ut} \notag \\
\hat{u_t}&= \rho_u \hat{u_{t-1}}+\varepsilon_{ut}
\end{align*}

14. Linearized Cost Push Shock: 
\begin{align*} \notag
\widehat{e}_{t}&= \rho_{e}\widehat{e}_{t-1} + \varepsilon_{et}
\end{align*}


An explanation of the variable can be found in appendix A.  
\newpage

# Data
This section will provide a brief discussion regarding the series of data and the subsequent transformation, as well as calibration of parameters and the estimated priors for the model. 

The model presented in the previous section is estimated with Bayesian estimation techniques using four key macroeconomic variables: output growth, inflation, short term nominal interest rate and nominal money growth. The series span from 1983:Q1 to 2019:Q4, thereby amounting to 151 observations. Following @belongia2019reconsideration, output is measured by the changes in the log of per capita real GDP; inflation is measured by changes in the log of the GDP deflator; nominal interest rates are measured by the annualized effective federal funds rate, which is convert to quarterly rates by dividing the series by 400 for each quarter, and last, the growth in nominal money is measured with changes in the per capita M2 index of monetary services. The data was collected on the FRED database of the Federal Reserve of St Louis. The data series used in the model are displayed below.

```{r}

plot_data <- obss %>% gather(name, data,-Date) %>% arrange(Date) %>% ggplot() + geom_line(aes(x =Date, y=data, color=name)) + facet_wrap(~name, scale="free_y") + ggthemes::scale_color_wsj() + labs(y = "Data", x = "Date", title = "Observable Data Series", subtitle= "Quarterly changes from 1982 to 2019", caption = "Source: fred.stlouisfed.org") + theme(legend.position="non")


plot_data
```

# Estimation 

## Calibration and Priors

To calibrate the model, I first calculated the logged first difference of the quarterly data to get stationary series. The average values over the entire sample period were calculated in order to obtain the parameter values for inflation (\(\pi\)), interest rate (\(r\)) and output growth (\(z\)). These values represent the steady state values as we manipulated the data to capture changes from the steady state. Using these values, the subjective discount rate (\(\beta\)) was calculated using the following formula:
\[ \beta = \Biggl(\frac{z}{r}\Biggl)\pi\]
Table \ref{tpar} below summarizes the parameter values that we calculate using our data. The values are used when simulating the models for each of the monetary rules. 

\begin{table} 
\caption{Parameters calculater using own data}
\begin{center}
\begin{tabular}{ |c|c| } 
 \hline
 Parameter & Value \\ 
 \hline
 \(\pi\)& 1.00128 \\ 
  \(r\)& 1.00978  \\ 
  \(z\) & 1.00039 \\
  \(\beta\) & 0.99197 \\
 \hline
\end{tabular}
\label{tpar}
\end{center}
\end{table}
Figure \ref{fig:prior1} and Figure \ref{fig:prior2} plots the prior distributions of the structural parameters, including the standard deviations of the shocks. The five structural shocks: \(\sigma_a\), \(\sigma_z\), \(\sigma_u\), \(\sigma_e\) and \(\sigma_r\) all have an inverse chi-square distribution with four degrees of freedom. @smets argued in favour of rather lose prior for the five shocks, and assigned the shocks inverse gamma distributions with two degree of freedom. However, @belongia2019reconsideration adjust this to allow the New Keynesian model to capture the increase in volatility after the 2008/2009 financial crises. 

\begin{table}
\caption{Exogenous Variables}
 \label{Table:enx}
 \begin{center}
\begin{tabular}{|c|c|} 
\hline
  Parameter & Description \\ 
\hline
 ${\sigma_a}$ & preference shock volatility\\
 ${\sigma_z}$ & productivity shock volatility\\
 ${\sigma_u}$ & money demand shock volatility\\
 ${\sigma_e}$ & cost push shock volatility\\
 ${\sigma_r}$ & monetary policy shock volatility\\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{figure}
\caption{(a) Prior Distributions}
\centering
\includegraphics[scale=0.5]{prior.jpg}
\label{fig:prior1}
\end{figure}

\begin{figure}
\caption{(b) Prior Distributions}
\centering
\includegraphics[scale=0.5]{prior_1.jpg}
\label{fig:prior2}
\end{figure}

Table \ref{Table:Prior} displays statistical characteristics of the priors. The habit formation (\(\gamma\)) and price indexation (\(\alpha\)) as well as the interest rate smoothing (\(\rho_r\)), preference shock persistence (\(\rho_a\)), money demand shock persistence (\(\rho_u\)) and cost push shock persistence (\(\rho_e\)) are constrained between zero and one by assigning a beta distribution to the parameters. To restrict the parameters to positive values, @belongia2019reconsideration assign gamma distributions for the Phillips curve slope (\(\psi\)), money demand adjustment semi-elasticity (\(\delta_r\)), money demand adjustment cost (\(\phi\)), policy response to inflation (\(\rho_\pi\)) and policy response to output gap (\(\rho_x\)). 

\begin{table}
\caption{Prior information (parameters)}
 \label{Table:Prior}
 \begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|} 
\hline
  &  &  & & & \multicolumn{2}{|c|}{Bounds} \\ 
  \cline{6-7}
  Symbol & Description & Distribution & Mean & Std.dev. & Lower & Upper \\ 
\hline
$ {\sigma_a} $ & preference shock volatility & Inv. Chi-squared & 0.0125  & 0.0066 & 0.0000 & $\infty$  \\ 
$ {\sigma_z} $ & productivity shock volatility & Inv. Chi-squared  & 0.0125 & 0.0066 & 0.0000 & $\infty$ \\ 
$ {\sigma_u} $ & money demand shock volatility & Inv. Chi-squared & 0.0125  & 0.0066 & 0.0000 & $\infty$  \\ 
$ {\sigma_e} $ & cost push shock volatility & Inv. Chi-squared & 0.0031 & 0.0016 & 0.0000 & $\infty$  \\ 
$ {\sigma_r} $ & monetary policy shock volatility & Inv. Chi-squared & 0.0031  & 0.0016 & 0.0000 & $\infty$  \\ 
$ {\gamma} $ & habit formation& Beta & 0.5000  & 0.2000 & 0.0000 & 1.0000 \\ 
$ {\alpha} $ & price indexation  & Beta & 0.5000 & 0.2000 & 0.0000 & 1.0000  \\ 
$ {\psi} $ & Phillips curve slope & Gamma & 0.1000 & 0.0300 & 0.0000 & $\infty$ \\ 
$ {\delta_r} $ & money demand semi-elasticity & Gamma & 15.0000  & 5.0000 & 0.0000 & $\infty$ \\ 
$ {\phi} $ & money demand adjustment cost & Gamma & 10.0000 & 10.0000 & 0.0000 & $\infty$  \\ 
$ {\rho_r} $ & interest rate smoothing & Beta & 0.7500 & 0.1000 & 0.0000 & 1.0000 \\ 
$ {\rho_\pi} $ & policy response to inflation & Gamma & 0.4000  & 0.1000 & 0.0000 & $\infty$  \\ 
$ {\rho_x} $ & policy response to output gap & Gamma & 0.2000 & 0.1000 & 0.0000 & $\infty$ \\ 
$ {\rho_a} $ & preference shock persistence  & Beta & 0.7500  & 0.1000 & 0.0000 & 1.0000  \\ 
$ {\rho_u} $ & money demand shock persistence & Beta & 0.7500  & 0.1000 & 0.0000 & 1.0000  \\ 
$ {\rho_e} $ & cost push shock persistence & Beta & 0.5000  & 0.1000 & 0.0000 & 1.0000  \\ 
\hline
\end{tabular}
\end{center}
\end{table}

It is important to note that although the distribution for the shocks are inverse chi-square, in the actual estimation, they are simulated as having inverse gamma distribution. This is because the chi-square prior is not implemented in \emph{dynare}. The chi-squared distribution is a special case of the gamma distribution, therefore it is possible to interchange between the two.


## Posterior Estimation

Table \ref{tab_post} displays statistical information about the posterior estimations for the Taylor rule and the flexible money growth rate rule. The posterior mean and mode between the two rules are very similar with the only noticeably large difference being the money demand adjustment cost (\(\phi\)), where under the flexible money growth rate rule it is twice as large. The standard deviation and the highest posterior denisty interval (HPDI) upper and lower bound remain relatively constant between the two rules, with, once again, the only exception being money demand adjustment cost (\(\phi\)). 

\begin{table}
\caption{Posterior Information - where HPD (L) and HPD (U) display the 90 percent Highest Posterior Density Interval Lower and Upper bound, respectively.}
 \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{9}{|c|}{Taylor Rule} \\
\cline{1-9}
\hline
 &  & \multicolumn{2}{|c|}{Prior} & \multicolumn{5}{|c|}{Posterior}\\ 
  \cline{8-9}
\hline
  Symbol & Distribution & Mean & Std.dev. & Mean & Mode & Std. dev & HPD (L) & HPD (U)\\ 
\hline
$ {\sigma_a} $ & Inv. Chi-squared & 0.0125 & 0.0066  & 0.0694 & 0.0665 & 0.0215 & 0.0064 & 0.0237 \\ 
$ {\sigma_z} $ & Inv. Chi-squared  & 0.0125  & 0.0066  & 0.0086 & 0.0067 & 0.0019 & 0.0064 & 0.0237 \\ 
$ {\sigma_u} $ & Inv. Chi-squared & 0.0125  & 0.0066 & 0.0699 & 0.0336 & 0.0326 & 0.0064 & 0.0237 \\ 
$ {\sigma_e} $ & Inv. Chi-squared & 0.0031  & 0.0016 & 9.511e-04 & 7.294e-04  & 2.041e-04 & 0.0016 & 0.0058 \\ 
$ {\sigma_r} $ & Inv. Chi-squared & 0.0031  & 0.0016 & 0.0013 & 0.0013 & 8.628e-05 & 0.0016 & 0.0058 \\ 
$ {\gamma} $ & Beta & 0.5000  & 0.2000 & 0.9496 & 0.9383 & 0.0133 & 0.1718 & 0.8282 \\ 
$ {\alpha} $ & Beta & 0.5000 & 0.2000 & 0.9006 & 0.9655 & 0.0590 & 0.1718 & 0.8282 \\ 
$ {\psi} $ & Gamma & 0.1000  & 0.0300 & 0.0350  & 0.0108 & 0.0174 & 0.0563 & 0.1539 \\ 
$ {\delta_r} $ & Gamma & 15.0000 & 5.0000 & 12.5553  & 7.8858  & 5.7152 & 7.8254 & 24.0577 \\ 
$ {\phi} $ & Gamma & 10.0000 & 10.0000 & 36.3493 & 12.0157 & 21.4019 & 0.5129 & 29.9573 \\ 
$ {\rho_r} $ & Beta & 0.7500 & 0.1000 & 0.9079 & 0.8985 & 0.0216 &  0.5701 & 0.8971 \\ 
$ {\rho_\pi} $ & Gamma & 0.4000  & 0.1000  & 0.9836 & 0.8030 & 0.1464 & 0.2509 & 0.5774 \\ 
$ {\rho_x} $ & Gamma & 0.2000  & 0.1000 & 0.2909 & 0.2948 & 0.1080 & 0.0683 & 0.3877 \\ 
$ {\rho_a} $ & Beta & 0.7500 & 0.1000  & 0.9889 & 0.9905 & 0.0048 & 0.5701 & 0.8971 \\ 
$ {\rho_u} $ & Beta & 0.7500  & 0.1000 & 0.9642 & 0.9919 & 0.0289 & 0.5701 & 0.8971 \\ 
$ {\rho_e} $ & Beta & 0.5000  & 0.1000 & 0.5926 &  0.2348 & 0.2444& 0.3351 & 0.6649 \\ 
\hline
\multicolumn{9}{|c|}{Flexible Money Growth Rule} \\
\cline{1-9}
$ {\sigma_a} $ & Inv. Chi-squared & 0.0125 & 0.0066  & 0.0638 & 0.0716 & 0.0135 & 0.0462 & 0.0851\\ 
$ {\sigma_z} $ & Inv. Chi-squared  & 0.0125  & 0.0066 & 0.0051 & 0.0046 &  4.604e-04 & 0.0043 & 0.0058 \\ 
$ {\sigma_u} $ & Inv. Chi-squared & 0.0125  & 0.0066 & 0.0073 & 0.0066 & 0.0015 & 0.0048 & 0.0094\\ 
$ {\sigma_e} $ & Inv. Chi-squared & 0.0031  & 0.0016 & 6.414e-04 & 635e-04 & 3.969e-05 &  5.760e-04 & 7.031e-04\\ 
$ {\sigma_r} $ & Inv. Chi-squared & 0.0031  & 0.0016 & - & - & - & - & -\\ 
$ {\gamma} $ & Beta & 0.5000  & 0.2000 & 0.9132 & 0.9055 & 0.0114 & 0.8931 & 0.9304 \\ 
$ {\alpha} $ & Beta & 0.5000 & 0.2000 & 0.8475 &  0.8436 & 0.0397 & 0.7789 & 0.9076\\ 
$ {\psi} $ & Gamma & 0.1000  & 0.0300 & 0.0038 & 0.0046 & 9.218e-04 & 0.0024 & 0.0054 \\ 
$ {\delta_r} $ & Gamma & 15.0000 & 5.0000 & 8.6681 & 8.1955 & 1.0702 & 6.9422 & 10.4597\\ 
$ {\phi} $ & Gamma & 10.0000 & 10.0000 & 68.35 & 65.6454 & 16.5853 & 39.4357 & 95.0324\\ 
$ {\rho_r} $ & Beta & 0.7500 & 0.1000 & 0.7637 & 0.7817 & 0.0886 & 0.6258 & 0.9141\\ 
$ {\rho_\pi} $ & Gamma & 0.4000  & 0.1000 & 0.3970 & 0.3750 & 0.0964 & 0.2480 & 0.5210\\ 
$ {\rho_x} $ & Gamma & 0.2000  & 0.1000 & 0.2003 & 0.1500 & 0.0939 & 0.0484 & 0.3420\\ 
$ {\rho_a} $ & Beta & 0.7500 & 0.1000  &  0.9902 & 0.9920 & 0.0019 & 0.9876 & 0.9932\\ 
$ {\rho_u} $ & Beta & 0.7500  & 0.1000 & 0.8574 & 0.8548 & 0.0496 & 0.7652 & 0.9277\\ 
$ {\rho_e} $ & Beta & 0.5000  & 0.1000 & 0.1189 & 0.1263 & 0.0247 & 0.0786 & 0.1579 \\ 
\hline
\end{tabular}
\end{center}
\label{tab_post}
\end{table}

## MCMC acceptance ratio

Since the DSGE model specified has more than five parameters, we would expect to see an acceptance ration of around 23 percent @bedard2008optimal. In my \emph{dynare} code, I set the number of Metropolis-Hastings Chains to two, which is the default and the number of iteration to 25 000. The acceptance ratios are all strictly positive and close the expected value. The Taylor rule and constant money growth rule are slightly above the expected average, and the flexible money growth rate rule acceptance ratio is slightly below.  

\begin{table}
\caption{MCMC acceptance ratio (precent)}
 \label{mcmc_acceptance}
 \begin{center}
\begin{tabular}{|c|c|c|c|} 
\hline
   & Taylor Rule & Flexible Money Growth rate Rule & Constant Money Growth Rule \\ 
\hline
 Chain 1 & 31.184 & 18.616 & 33.192 \\
 Chain 2 & 35.176 & 17.228 & 33.784 \\
\hline
\end{tabular}
\end{center}
\end{table}

## Blanchard-Khan Stability Conditions

The assumption that macroeconomic models assume perfect foresight has been widely critiqued. However, the assumption has been made possible due to improvement of simulation algorithms. For the model to have a unique solution, the Blanchard-Khan conditions have to be met. These conditions are easy to check, in terms of eigenvalues computed at the steady state of the model @laffargue2000blanchard.  This unique solution  for the model is determined if and only if the number of unstable eigenvalues is equal to the number of non-predetermined variables. The Blanchard-Khan condition for the DSGE model of this project is satisfied as there are five eigenvalues larger than one in the modulus for five forward looking variables in the model. 

## Bayesian Impulse Response functions

Much research in macroeconomics have been done to understand the relative impact of different shock on aggregate economic activity. Analyzing the bayesian Impulse response functions, the Taylor rule seems to deliver better results given a
shock to preferences and productivity, while the flexible money growth rule delivers similar-to-better results for the money demand and cost push shocks. The IRFs that we simulated look very similar to @belongia2019reconsideration in shape. 

The gray shaded area reflects the highest posterior density interval (HPDI). A description of the variables can be found in table \ref{Table:end} under appendix A. 

### Preference Shock 
Figure \ref{tay_a} and Figure \ref{flex_a} represents the impulse response functions as a results of a preference shock to the variables in the model for the Taylor rule and the flexible money growth rule, respectively. Preference shock can be interpreted as a shock to household production, since it will affect household behaviour by affecting savings-consumption decisions. 

A positive preference shock leads to an increase in labour supply and decrease in leisure, which in turn leads to an increase in initial output and consumption. Consequently, we would expect to see that savings and investment decrease. After prices and wages adjust, the output growth slowly returns to its steady state. 

In figure \ref{tay_a} and Figure \ref{flex_a}, an initial spike in inflation can be seen. This is due to the increase in output and labour supply. However, inflation returns to its steady state faster under the Taylor rule. The Taylor rule and the flexible monetary policy growth rule have similar responses, with the flexible monetary policy rule being more volatile to changes in output gap (\(x\)) and money growth (\(\mu\)) and therefore taking longer to return to its steady states values.  

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_a1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_a2.jpg} 
	\end{minipage}
	\caption{Orthogonalized Shock to Preference Shock - Taylor Rule}
	\label{tay_a}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_a1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_a2.jpg} 
	\end{minipage}
	\caption{Orthogonalized Shock to Preference Shock - Flexible Money Growth Rule}
	\label{flex_a}
\end{figure}


### Productivity Shock (z)
Figure \ref{tay_z} and Figure \ref{flex_z} represents the impulse response functions as a results of a productivity shock to the variables in the model for the Taylor rule and the flexible money growth rule, respectively.  A positive productivity shock is expected to persist over time, although not permanently. Therefore, a productivity shocks leads to an increase in  hours worked and real wage which in turn increase output, consumption and investment. The increase in output would then lead to an increase in money growth, as it would be necessary to increase money printing. 

The flexible money growth rules better reflects what we theoretically would expect to see when a productivity shock occurs. Figure \ref{tay_z} and \ref{flex_z} support the view that productivity shocks play an important roles in accounting for fluctuations in output. Furthermore, it supports the view that technology shocks affect the marginal product of labour and the marginal product of capital. 

\begin{figure}
\centering
\includegraphics[scale=0.3]{tay_z.jpg}
\caption{Orthogonalized Shock to Productivity Shock - Taylor Rule}
\label{tay_z}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_z1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_z2.jpg} 
	\end{minipage}
	\caption{Orthogonalized Shock to Productivity Shock - Flexible Money Growth Rule}
	\label{flex_z}
\end{figure}

### Money Demand Shock (u)
Figure \ref{tay_u} and Figure \ref{flex_u} represents the impulse response functions as a results of a money demand shock to the variables in the model for the Taylor rule and the flexible money growth rule, respectively. Money demand shocks are more likely to lead to volatility in inflation and output. This results can be seen in figure \ref{flex_u}, which shows that output (\(\hat{y}\)), consumption (\(c\)), inflation (\(\pi\)), output gap (\(x\)) and money growth (\(\mu\)) all follow volatility and similar paths. The rise in the demand for money is temporarily followed by an increase in the growth rate of money (\(\mu\)), which in turn exerts upward pressure on inflation (\(\pi\)), as can be seen in in figure \ref{flex_u}. 

\begin{figure}
\centering
\includegraphics[scale=0.5]{tay_u.jpg}
\caption{Orthogonalized Shock to Money Demand Shock - Taylor Rule}
\label{tay_u}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_u1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_u2.jpg} 
	\end{minipage}
	\caption{Orthogonalized Shock to Money Demand Shock - Flexible Money Growth Rule}
	\label{flex_u}
\end{figure}

### Cost Push Shock (e)

Cost push shocks are transitory deviations between the flexible price equilibrium and efficient allocation. Cost push shocks create a increase in inflation and a decrease in output gap, simultaneous. Therefore, the optimal response of the central bank is extremely controversial. The central bank can make one of two contradicting choices; it can either relax its monetary policy in order to accommodate the negative output gap, or it can tighten its monetary policy in order to combat the increase inflation.  Figure \ref{tay_e} and Figure \ref{flex_e} represents the impulse response functions as a results of a cost push shock to the variables in the model for the Taylor rule and the flexible money growth rule, respectively. 

The Taylor rule and the flexible money growth rate rule are comparatively similar. This implies that the flexible money growth rate rule can be used as an alternative to the Taylor rule give most of the shocks.


\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_e1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_e2.jpg} 
	\end{minipage}
	\caption{Orthogonalized Shock to Cost Push Shock - Taylor Rule}
	\label{tay_e}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_e1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_e2.jpg} 
	\end{minipage}
	\caption{Orthogonalized Shock to Cost Push Shock - Flexible Money Growth Rule}
	\label{flex_e}
\end{figure}

# Evaulation
Many resources and time has been dedicated to find the optimal rule to advise monetary policy rules. An optimal monetary policy rule is designed in such a manner as to stabilize prices and output as well as boost consumer confidence. In this section, several diagnostic test are carried out in order to analyze the empirical fit of the DSGE model in terms of the Taylor rule and the flexible money growth rule. The Taylor rule and flexible money growth rule will be analyzed and compared, with some reference being made to the constant money growth rule. 


## Mode Plots 
Figure \ref{mode_tay} and \ref{mode_flex} display the mode check plots for the taylor rule and the flexible money growth rule, respectively. The difference in the shapes of the likelihood kernel (red line) and the posterior likelihood (blue line) indicates the role of the prior in influencing the curvature of the likelihood function. As can be seen in the plots, the mode is at the maximum point of the posterior likelihood. This implies that there are no  identification problems. The red dots on the figures indicates a violation of the Blanchard-Kahn conditions and the model could not solve those parameter values.  

There are slight difference between the taylor rule and the flexible money growth rule mode check plots. These differences are due to the observed money growth being included in the taylor rule but not the flexible money growth rate rule. 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{taylor.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{taylor1.jpg} 
	\end{minipage}
	\caption{Mode Check Plots - Taylor Rule}
	\label{mode_tay}
\end{figure} 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex1.jpg} 
	\end{minipage}
	\caption{Mode Check Plots - Flexible Money Growth Rule}
	\label{mode_flex}
\end{figure} 

## Monte Carlo Markov Chain univariate diagnostics

It is extremely challenging to test for the convergence of the posterior distribution. However, \emph{dynare} provides us with Monte Carlo Markov Chain (MCMC) univariate diagnostics which makes it easier to analyze. Figure \ref{mcmctay}, \ref{mctay12}, \ref{mctay34} and \ref{mctay56} as well as figure \ref{mcflex}, \ref{mcflex12}, \ref{mcflex34}, \ref{mcflex5} represents convergences indicators for all parameters considered for the Taylor rule and the flexible money growth rule. 

There are three plots for each parameter. The first plot shows the convergence diagnostics for the 80 percent interval. The second plot shows the estimate of the second central moment (m2), the variance, and the third plot shows the estimate of the third central moment (m3). The red line shows the 80 percent quantile range based on the pooled draws from all sequences and the blue line shows the mean interval range based on the draws of the individual sequences. The plots can be interpreted as the chains having converged if the red and blue line stabilize horizontally and remain close to each other.

I expect to see that many of the iterations of the Metropolis-Hasting simulating to be similar, meaning that for the results to be sensible, I would expect to see the red and blue lines remain relatively constant and they should converge. Studying the results for the Taylor rule, I find mixed results. Preference shock volatility (\(\sigma_a\)), productivity shock volatility (\(\sigma_z\)), monetary policy shock volatility (\(\sigma_r\)), price indexation (\(\alpha\)), Interest rate smoothing (\(\rho_r\)), policy response to inflation (\(\rho_\pi\)), policy response to output gap (\(\rho_x\)) and preference shock persistence (\(\rho_a\)) all seem to all converge, especially in relation \emph{interval}. However, the other eight variables show greater variation during the process of convergence. This unsatisfactory performance for the estimation of these parameters is related to the prior values for each as they show weak identification. This is concerning since the the general results displayed in figure \ref{mcmctay} is considered unsatisfactory, implying that the prior might need reconsideration. Figure \ref{mcmctay} also shows that the parameters converge to the target distribution at around 10 000 iterations, after which they drastically diverge again. 

However, the flexible money growth rate rule shows much more promising and satisfactory results. The only parameter that does not converge is the preference shock persistence (\(\rho_a\)). The results are extremely satisfactory, implying that that is no reasons to change the prior values. Figure \ref{mccon} shows that the general results for the constant money growth rule is similar to that of the flexible money growth rate rule, however, it seems to diverge at 4000 iterations before it converges again at 7000 iterations. The divergence implies that the flexible money growth rate is more stable than the constant money growth rate. This suggest that the flexible money growth rule could lead to a more stable and predicable path of the parameters. Thus, taking only the MCMC univariate diagnostics into account, I conclude that the flexible Money growth rule is more optimal given the information in the observed data.   

\begin{figure}
\caption{MCMC general - Taylor Rule}
\centering
\includegraphics[scale=0.5]{mcmctay.jpg}
\label{mcmctay}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mctay1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mctay2.jpg} 
	\end{minipage}
	\caption{(a) MCMC - Taylor Rule}
	\label{mctay12}
\end{figure} 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mctay3.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mctay4.jpg} 
	\end{minipage}
	\caption{(b) MCMC - Taylor Rule}
	\label{mctay34}
\end{figure} 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mctay5.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mctay6.jpg} 
	\end{minipage}
	\caption{(c) MCMC - Taylor Rule}
	\label{mctay56}
\end{figure} 

\begin{figure}
\caption{MCMC general - Flexible Money Growth Rate Rule}
\centering
\includegraphics[scale=0.5]{mcflex.jpg}
\label{mcflex}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mcflex1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mcflex2.jpg} 
	\end{minipage}
	\caption{(a) MCMC - Flexible Money Growth Rate Rule}
	\label{mcflex12}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mcflex3.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{mcflex4.jpg} 
	\end{minipage}
	\caption{(b) MCMC - Flexible Money Growth Rate Rule}
	\label{mcflex34}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.3]{mcflex5.jpg}
\caption{(c) MCMC general - Flexible Money Growth Rate Rule}
\label{mcflex5}
\end{figure}

\begin{figure}
\caption{MCMC general - Constant Money Growth Rule}
\centering
\includegraphics[scale=0.5]{mccon.jpg}
\label{mccon}
\end{figure}

## Prior-Posterior Plot

Understanding the impact that the prior distribution has on the posterior density is very important. The impact of the priors is is extremely important to the model complexity and the structure of the data. Figure \ref{tay_pp} and figure \ref{flex_pp} display the relationship between the prior and the posterior. The gray line shows the prior distribution that is also displayed in figure \ref{fig:prior1} and figure \ref{fig:prior2}. The black line shows the density of the posterior distribution and the green line shows the posterior mode. Figure \ref{tay_pp} shows the prior and posterior plots for the Taylor rule. All the plots prior and posterior distributions are vastly different, except for money demand semi-elasticity (\(\delta_r\)) and policy response to output gap (\(\rho_x\)). This can be due to the fact the prior is an very accurate reflection of the information in the data. However, more likely, it is due to that fact that (\(\rho_x\)) and (\(\delta_r\)) are only weakly identified and that the data proves limited information to update the prior.

Figure \ref{flex_pp} displays the prior and posterior plots for the flexible money growth rule. The prior and posterior distributions of interest rate smoothing (\(\rho_r\)), policy response to inflation (\(\rho_\pi\)) and policy response to output gap (\(\rho_x\)) are extremely similar. This is of concern as it is an indication that the parameters were only weakly identified. 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_pp1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_pp2.jpg} 
	\end{minipage}
	\caption{Priors and Posterior: Taylor Rule}
	\label{tay_pp}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_pp1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_pp2.jpg} 
	\end{minipage}
	\caption{Prior and Posterior: Flexible Money Growth Rule}
	\label{flex_pp}
\end{figure}

## Smoothed Shocks 

Smoothed shocks are a reconstructions of the best estimate of the values of the unobserved shocks over the entire sample period, using the observed data. Figure \ref{smooth} show that the structural shocks to both the Taylor rule and the flexible money growth rule are stationary around a mean of zero (the red line). 

Figure \ref{smooth} shows a significant shock at around 75 periods for preference  and productivity shock for both rules. This volatility represents the 2001 recession, where a decline in economic activity was short lived and occurred mainly in developed countries. Further volatility can be seen around 110 periods for money demand shock, cost push shock and preference shock, representing the 2007/2008 financial crisis. The monetary policy shock in the Taylor rule seems to be relatively stable. Preference shocks seem to be more volatile under the flexible money growth rule. However, the general results remain that the flexible money growth rule and Taylor rule estimate similar volatility of the respective shocks. 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_smooth.jpg} 
		\caption{Taylor Rule}
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_smooth.jpg} 
		\caption{Flexible Monetary Policy Rule}
	\end{minipage}
	\caption{Smoothed shocks}
	\label{smooth}
\end{figure}

## Historical and Smooth Variables

Figure \ref{hs} represent historical and smoothed variable plots. The analysis is done is order to determine whether measurement error exist in our model. The dotted black line represents the actual data that is observed and the red line represents the estimate of the smoothed variable. Under the Taylor rule and flexible money growth rate rule both series are identical as they overlap eachother, implying that there is no measurement error and that model is specified correctly. This is another indication that the flexible money growth rate rule preforms just as well as the Taylor rule. 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_hs.jpg} 
		\caption{Taylor Rule}
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_hs.jpg} 
		\caption{Flexible Monetary Policy Rule}
	\end{minipage}
	\caption{Historical and Smooth Variables}
	\label{hs}
\end{figure}

## Variance Decomposition 

The variance decomposition displayed in table \ref{tay_var_dec} and table \ref{flex_var_dec} is used to analyze how variation in the model is generated by a specific shock. This method is informative in establishing the relative importance of a specific shock as a source of volatility to a macroeconomic variable. Productivity shocks accounts for most of the variation in Consumption (\(c\)), output (\(\hat{y}\)) and the efficient level of output (\(\hat{q}\)) under the Taylor rule and the flexible money growth rule. Whereas a cost push shock accounts for most of the variation in inflation (\(\pi\)). Variation in monetary policy shock (\(r\)) is explained mostly by preference shock [60.86 percent and 51.09 percent], with cost push shock also explaining a large portion of the variation in the Taylor rule and flexible money growth rule, respectively. 

Under the Taylor rule, variation in money growth (\(\mu\)) and money demand (\(\hat{m}\)) is largely explained by a monetary demand shock. However, under the flexible money growth rule, money demand (\(\hat{m}\)) is mostly explained by a preference shock and money growth (\(\mu\)) is explained by similar by a preference shock, productivity shock and cost push shock. 

\begin{table}
\caption{Taylor Rule: Posterior Mean Variance Decomposition (in percent)}
 \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
  & Description &   ${\sigma_a}$  &  ${\sigma_z}$ & ${\sigma_u}$ & ${\sigma_e}$ & ${\sigma_r}$\\
\hline
${c}$ & consumption & 82.04 & 17.81 & 0.00 & 0.14 & 0.00 \\
 ${\hat y}$  & output & 82.04 & 17.81 & 0.00 & 0.14 & 0.00 \\
 ${\lambda}$ & lambda & 99.38 & 0.00 & 0.00 & 0.60 & 0.02 \\
${a}$ & preference shock & 100.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
${z}$ & productivity shock & 0.00 & 100.00 & 0.00 & 0.00 & 0.00 \\
 ${r}$ & monetary policy shock & 60.86 & 0.00 & 0.00 & 30.33 & 8.80 \\
${\pi}$ & inflation & 17.85 & 0.00 & 0.00 & 72.23 & 9.91 \\
${\hat q}$ & efficient level of output & 82.13 & 17.87 & 0.00 & 0.00 & 0.00 \\
 ${x}$ & output gap & 0.99 & 0.00 & 0.00 & 98.21 & 0.80 \\
${e}$ & cost push shock & 0.00 & 0.00 & 0.00 & 100.00 & 0.00 \\
${u}$ & money demand shock & 0.00 & 0.00 & 100.00 & 0.00 & 0.00 \\
${\hat m}$ & money demand & 9.69 & 0.51 & 87.62 & 3.99 & 1.31\\
${\mu}$  & money growth & 1.83 & 3.25 & 89.62 & 3.99 & 1.31 \\
${\hat g}$ & output growth & 49.20 & 49.00 & 0.00 & 1.75 & 0.05\\
\hline
\end{tabular}
\end{center}
\label{tay_var_dec}
\end{table}

\begin{table}
\caption{Flexible Monetary Policy Rule: Posterior Mean Variance Decomposition (in percent)}
 \begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
  & Description &   ${\sigma_a}$  &  ${\sigma_z}$ & ${\sigma_u}$ & ${\sigma_e}$ \\ 
\hline
${c}$ & consumption & 89.54 & 10.36 & 0.02 & 0.08 \\
 ${\hat y}$  & output & 89.54 & 10.36 & 0.02 & 0.08 \\
 ${\lambda}$ & lambda & 99.87 & 0.06& 0.02 & 0.05 \\
${a}$ & preference shock & 100.00 & 0.00 & 0.00 & 0.00 \\
${z}$ & productivity shock & 0.00 & 100.00 & 0.00 & 0.00 \\
 ${r}$ & monetary policy shock & 51.09 & 12.88 & 9.23 & 26.80 \\
${\pi}$ & inflation & 6.73 & 7.69 & 1.31 & 84.27 \\
${\hat q}$ & efficient level of output & 90.64 & 9.36 & 0.00 & 0.00 \\
 ${x}$ & output gap & 27.43 & 32.38 & 6.40 & 33.79 \\
${e}$ & cost push shock & 0.00 & 0.00 & 0.00 & 100.00 \\
${u}$ & money demand shock & 0.00 & 0.00 & 100.00 & 0.00 \\
${\hat m}$ & money demand & 74.40 & 17.01 & 1.52 & 7.08 \\
${\mu}$  & money growth & 25.09 & 33.15 & 3.44 & 38.33 \\
${\hat g}$ & output growth & 52.27 & 44.91 & 0.68 & 2.13 \\
\hline
\end{tabular}
\end{center}
\label{flex_var_dec}
\end{table}

## Forecasting 

Figure \ref{tay_mean} and figure \ref{flex_mean} displays the mean forecast plots of the Taylor rule and flexible money growth rule, respectively. The black line represents the mean forecasts of the macroeconomic endogenous variable, starting at the last observation in the sample and going 40 periods ahead. The green lines represent the mean forecast deciles. It is important to note that the forecasts only take parameter uncertainty into account and not the uncertainty about future shocks. Under the flexible money growth rule, the macroeconomic variable appear to stabilize to their steady state faster than the under the Taylor rule. This, once again, established that the flexible money growth rule could be more optimal than the Taylor rule. 


\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_fore_mean.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_fore_mean1.jpg} 
	\end{minipage}
	\caption{Forecasted Variables (mean) - Taylor Rule}
	\label{tay_mean}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_fore_mean.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_fore_mean1.jpg} 
	\end{minipage}
	\caption{Forecasted Variables (mean) - Flexible Money Growth Rule}
	\label{flex_mean}
\end{figure}

Figure \ref{tay_point} and figure \ref{flex_point} displays the point forecast plots for the Taylor rule and flexible money growth rule, respectively. In contrast to the mean forecast, the point forecast takes the parameter uncertainty and the uncertainty about future shocks into account. Both rules have very similar results, with the exception being the output gap (\(x\)) and the money demand shock (\(u\)), which both appear to stabilize around the steady state faster under the flexible money growth rule. 

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_fore_var1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{tay_fore_var2.jpg} 
	\end{minipage}
	\caption{Forecasted Variables (point) - Taylor Rule}
	\label{tay_point}
\end{figure}

\begin{figure}
	\centering 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_fore_var1.jpg} 
	\end{minipage} 
	\hspace{0.1cm} 
	\begin{minipage}[t]{8.2cm} 
		\centering 
		\includegraphics[width=\linewidth]{flex_fore_var2.jpg} 
	\end{minipage}
	\caption{Forecasted Variables (point) - Flexible Money Growth Rule}
	\label{flex_point}
\end{figure}


# Conclusion 

The central object of this project was to estimate, simulate and analyze the effect of the Taylor rule and flexible money growth rate rule on macroeconomic variables. Following @belongia2019reconsideration, this projects makes of the DSGE model and was estimated using a Bayesian approach. The overall findings indicate that the flexible money growth rule comparatively similar, and in some cases better, than the Taylor rule. This implies that policymakers should consider a flexible money growth rate rule since it successfully decreases macroeconomic volatility in inflation and output growth.

In the previous report, the conclusion was reach that the constant money growth rule preformed the poorest in the simulations, therefore, only it was only briefly mentioned. However, it remains clear that a reconsideration of the Fed’s monetary policy toolkit is warranted, and further study along this avenue should be encouraged.

\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

\begin{table}
\caption{Endogenous Variables}
 \label{Table:end}
 \begin{center}
\begin{tabular}{|c|c|c|} 
\hline
  Variable & Symbol & Description \\ 
\hline
\texttt{c} & ${c}$ & consumption\\
\texttt{yhat} & ${\hat y}$ & output\\
\texttt{lambda} & ${\lambda}$ & lambda\\
\texttt{a} & ${a}$ & preference shock\\
\texttt{z} & ${z}$ & productivity shock\\
\texttt{r} & ${r}$ & monetary policy shock\\
\texttt{pi} & ${\pi}$ & inflation\\
\texttt{qhat} & ${\hat q}$ & efficient level of output\\
\texttt{x} & ${x}$ & output gap\\
\texttt{e} & ${e}$ & cost push shock\\
\texttt{u} & ${u}$ & money demand shock\\
\texttt{mhat} & ${\hat m}$ & money demand\\
\texttt{mu} & ${\mu}$ & money growth\\
\texttt{ghat} & ${\hat g}$ & output growth\\
\texttt{gobs} & ${g^{obs}}$ & observed output growth\\
\texttt{piobs} & ${\pi^{obs}}$ & observed inflation\\
\texttt{robs} & ${r^{obs}}$ & observed interest rate\\
\texttt{muobs} & ${\mu^{obs}}$ & observed money growth\\
\hline
\end{tabular}
\end{center}
\end{table}



\begin{table}
\caption{Parameters}
 \label{Table:para}
 \begin{center}
\begin{tabular}{|c|c|c|} 
\hline
  Variable & Symbol & Description \\ 
\hline
\texttt{z\_ss} & ${z_{ss}}$ & output growth steady state\\
\texttt{beta} & ${\beta}$ & discount factor\\
\texttt{gamma} & ${\gamma}$ & habit formation\\
\texttt{rho\_a} & ${\rho_a}$ & preference shock persistence\\
\texttt{alpha} & ${\alpha}$ & price indexation\\
\texttt{psi} & ${\psi}$ & Phillips curve slope\\
\texttt{rho\_r} & ${\rho_r}$ & interest rate smoothing\\
\texttt{rho\_pi} & ${\rho_\pi}$ & policy response to inflation\\
\texttt{rho\_x} & ${\rho_x}$ & policy response to output gap\\
\texttt{delta\_r} & ${\delta_r}$ & money demand semi-elasticity \\
\texttt{phi} & ${\phi}$ & money demand adjustment cost\\
\texttt{r\_ss} & ${r_ss}$ & interest rate steady state\\
\texttt{rho\_u} & ${\rho_u}$ & money demand shock persistence\\
\texttt{rho\_e} & ${\rho_e}$ & cost push shock persistence\\
\texttt{rho\_mm} & ${\rho_mm}$ & money shock\\
\texttt{rho\_mpi} & ${\rho_m\pi}$ & money inflation shock\\
\texttt{rho\_mx} & ${\rho_mx}$ & output gap shock\\
\hline
\end{tabular}
\end{center}
\end{table}



